Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
Fix typo.
more deps in graph

\begin{center}
{\footnotesize
\begin{tikzpicture}[>=stealth',semithick]

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (goedel) { Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2cm] (cantor) { Cantor };
\end{scope}

@@

\end{tikzpicture}
}
\end{center}

@@

\section{Modernizing the infrastructure}

@@

\section{Acknowledgments}
\label{sect:acks}
We are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russel O'Connor(Goedel), Matthieu Sozeau (Equations), the Mathematical Components team (ssreflect, algebra), Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers
of \coq and its associated tools.

>>>>

\begin{figure}[h]
\centering
{\footnotesize
\begin{tikzpicture}[thick]

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };    
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };
\end{scope}

@@

\draw[->,dotted] (additions.south) -- (chains.north west) ;
\draw[->] (goedel) -- (goedelcc) ;
\draw[->] (goedel) -- (hydras.north west) ;
\draw[->] (cantor) -- (hydras.north) ;
\draw[->] (cantor.south) -- (gaia.north west) ;
\draw[->] (hydras) -- (gaiahydras) ;
\draw[->] (gaia.south west) -- (gaiahydras) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:round}
\end{figure}

In mainstream software, it is common for packages to continually depend on a large number of packages. In contrast, projects in the Coq ecosystem are often subject to ``dependency aversion'', where maintainers eschew depending on useful packages because it may lead to work in adapting to upstream changes. With \Hydras, we hope to demonstrate that projects with complex dependencies are feasible to manage using recent advances in build management and infrastructure.

@@

\section{Modernizing the building infrastructure}

@@

\section{Acknowledgments}
\label{sect:acks}
We are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russell O'Connor (Goedel), Matthieu Sozeau (Equations), the Mathematical Components team, Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers of \coq and its associated tools.
